Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Update todo
Update introduction disposition

@@

@@

% Thursday:
% TODO: Reference labels
% TODO: Fix citings like they appear in the example thesis
% TODO: Abstract: Mention that the scientific study is a contribution

% TODO: Introduction (See meeting log for suggestions)
    % TODO: Introduction, picture of a virtual city
    % TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
    % TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

>>>>

Description of the field of city reproduction (Parish Müller).

@@

Viewpoints can range from modelling individual roads (find reference) and building facades (todor) to looking at entire city parcels and how they connect with each other (find reference).

Description of procedural modelling of cities (find reference).

@@

% Thursday:
% TODO: Fix citings like they appear in the example thesis

% TODO: Introduction disposition (See meeting log for suggestions)
    % TODO: Introduction, picture of a virtual city
    % TODO: Main challenge: How to reconstruct a 3D city. Make this more clear in the abstract
    % TODO: 2.1: Add a sentence about where the question fits into the big picture
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture
